---
title: "Reverse Engineering Project" https://fivethirtyeight.com/features/women-in-comic-books/

author: Steven Adriana Andrea 
date: October 8, 2023
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, [STORY NAME](STORY URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(janitor)
library(readr)
library(refinr)

```

## Load and Cleaning Data


In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data


# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

dc_data <- read_csv("data/dc-wikia-data.csv")
marvel_data <- read_csv("data/marvel-wikia-data.csv")

dc_womenincomics2014_comparedto2013 <- read_csv("data/DC 2014 Women In Comics Stats.csv")
marvel_womenincomics2014_comparedto2013 <- read_csv("data/MARVEL 2014 Women In Comics Stats.csv")

dc_womenincomics2014_month <- read_csv("data/MONTH DC Women In Comics 2014.csv")
marvel_womenincomics2014_month <- read_csv("data/MONTH MARVEL Women In Comics 2014.csv")

# Clean required data and prepare for analysis if needed. 

clean_dc <- clean_names(dc_data)

clean_marvel <- clean_names(marvel_data)

```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: Women were substantially underrepresented among characters with at least one appearance. Among the characters for which we have gender data, 12 females made up only 29.3 percent of the DC character list and 24.7 percent of the Marvel roster.
* **Analysis summary**: In our replication of the findings, we found the representation of women in comics is actually a little lower than the percentage the author found for each comic company. Hickey stated that women made up only 29.3% of the DC character list, and we were able to confirm this number when we excluded characters that could not have a gender (ex. a space ship). Hickey also stated that women made up 24.7%, which we were also able to confirm using the same methods.

```{r}
# Put code to reverse engineer sentence here

dc_gender <- clean_dc |> 
  filter(!is.na(sex), appearances >= 1) |> 
  group_by(sex) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))

```

```{r}

marvel_gender <- clean_marvel |> 
  filter(!is.na(sex), appearances >= 1) |> 
  group_by(sex) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))
```


```{r}
# Display results of code below this codeblock
 
view(dc_gender)
view(marvel_gender)
```




### Sentence 2

* **Sentence text**: Publishing houses have also sought to introduce more gay, lesbian, bisexual and transgender characters into their stories. In some cases, both DC and Marvel have retroactively categorized a longstanding character as LGBT.
* **Analysis summary**: We found in our findings that LGBTQ+ characters in Marvel had a little bit of a boom in the 2000s. Every year from 2000-2013 introduced a new LGBTQ+ character. There were even a few in the 1990s, 80s and 70s, though one wasn’t introduced each year. Four LGBTQ+ characters were introduced in the 40s and then none were introduced in the 50s. For DC Comics, a new LGBTQ+ character isn’t introduced each year from 2000-2010, but there is typically more than one introduced during the represented years. There were five LGBTQ+ characters introduced in 1987, 1988 and 1989 – something that didn’t happen again until 2003. It is unclear if the LGBTQ+ characters in the earlier years were ones that were planned to be LGBTQ+ or if they were retroactively categorized as such.


```{r}
# Put code to reverse engineer sentence here
dc_LGBT <- clean_dc |>
  filter(!is.na(gsm))


dc_girls_gays_and_theys <- dc_LGBT |>
  group_by(year) |>
  summarise(
    count_year=n()
  )

marvel_LGBT <- clean_marvel |>
  filter(!is.na(gsm))


marvel_girls_gays_and_theys <- marvel_LGBT |>
  group_by(year) |>
  summarise(
    count_year=n()
  )
```


```{r}
# Display results of code below this codeblock

view(dc_girls_gays_and_theys)

view(marvel_girls_gays_and_theys)
```

### Sentence 3

* **Sentence text**: Women and men were almost exactly equally likely to have a secret identity in the Marvel universe (49.4 percent of males and 49.5 percent of females), while in the DC universe 51 percent of males had a secret identity and 45 percent of females did.

* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

Like sentence 1, we had to take out the characters that could not have a gender as well as the characters that could not have a secret identity (we figured these were more of background/filler characters). Once we took out those characters, we were able to come to the same conclusion as Hickey. The Marvel one was slightly different. We still ended up with 49.4 percent of males but 49.4 percent for females as well instead of 49.5.


```{r}
# Put code to reverse engineer sentence here

#Who are the people with no ID?

no_id <- clean_dc |> 
  filter(is.na(id))

no_id

# They are more side characters than heroes. We can likely exclude them from the code to get to the author's main findings

# Here we're looking for the secret identity split up in DC Comics
dc_secret_identity <- clean_dc |> 
filter(!is.na(sex),
       (!is.na(id))) |> 
group_by(sex, id) |> 
summarise(count=n()) |> 
mutate(percentage = (count/sum(count)*100)) |> 
arrange(desc(count))

# Now for Marvel
marvel_secret_identity <- clean_marvel |> 
  filter(!is.na(id),
       (!is.na(id))) |> 
group_by(sex, id) |> 
summarise(count=n()) |> 
mutate(percentage = (count/sum(count)*100)) |> 
arrange(desc(count))
```

```{r}
# Display results of code below this codeblock
view(dc_secret_identity)
view(marvel_secret_identity)
```

### Sentence 4

* **Sentence text**: “When we zero in on the 2,415 DC and 3,342 Marvel characters with gender data who appear at least 10 times — the set of characters that probably gives the most consistent view of what we see on the page — female characters make up only 30.9 percent of the DC universe and 30.6 percent of the Marvel universe.”
 
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here
# To arrive at the totals, we had to filter out the characters that did not have gender data. Which means instead of 2,415 DC characters and 3,342 Marvel characters, these percentages are out of 2,386 DC and ___ Marvel characters



DC_10_appearances <- clean_dc |> 
  #Add a mutate column for percentage
  filter(!is.na(sex), appearances >= 10) |> 
  group_by(sex) |> 
  summarise(count = n()) |> 
  mutate(percentage = (count/sum(count)*100)) |> 
  arrange(desc(count))

DC_10_appearances

#clean_marvel






# Display results of code below this codeblock
```



### Sentence 5

* **Sentence text**: In both DC and Marvel, women were of neutral allegiance at a higher rate than men. Men were also more likely to be bad in each universe — in fact, bad-aligned men alone outnumbered all women combined. In other words, there’s something of a paucity of female villains.
* **Analysis summary**: We found that it holds true that women were less likely to have an evil alignment than men but were more likely to be neutral in both DC and Marvel comics. The original data and our data compare alignment within the sex category.
We found the following statistics with the data:
DC:
Evil men: 46.1%
Evil women: 30.2%
Neutral men: 7.7%
Neutral women: 10.2%

Marvel:
Evil men: 46.4%
Evil women: 25.7%
Neutral men: 12.4%
Neutral women: 17%



```{r}
# Put code to reverse engineer sentence here
clean_dc |> 
  filter(appearances >= 1) |> 
  group_by(sex, align) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))

clean_marvel |> 
  filter(appearances >= 1) |> 
  group_by(sex, align) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))


```

```{r}
# Display results of code below this codeblock


```

-30-