---
title: "Reverse Engineering Project"
author: "Student names here"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, [STORY NAME](STORY URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(janitor)
library(readr)
library(refinr)

```

## Load and Cleaning Data


In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data


# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

dc_data <- read_csv("data/dc-wikia-data.csv")
marvel_data <- read_csv("data/marvel-wikia-data.csv")

# Clean required data and prepare for analysis if needed. 

clean_dc <- clean_names(dc_data)

clean_marvel <- clean_names(marvel_data)

```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: Women were substantially underrepresented among characters with at least one appearance. Among the characters for which we have gender data,12 females made up only 29.3 percent of the DC character list and 24.7 percent of the Marvel roster.
* **Analysis summary**: In our replication of the findings, we found the representation of women in comics is actually a little lower than the percentage the author found for each comic company. Hickey stated that women made up only 29.3% of the DC character list but we found in the data that they only represented 23.6% of DC characters. Hickey also stated that women made up 24.7% of the Marvel roster but we found that they only accounted for 23.6%. 
```{r}
# Put code to reverse engineer sentence here

clean_dc |> 
  filter(appearances >= 1) |> 
  group_by(sex) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))
```
```{r}

clean_marvel |> 
  filter(appearances >= 1) |> 
  group_by(sex) |> 
   summarise(
    count=n()) |> 
  arrange(desc(count)) |> 
  mutate(percentage = (count/sum(count)*100))

# Display results of code below this codeblock

```

### Sentence 2

* **Sentence text**: Publishing houses have also sought to introduce more gay, lesbian, bisexual and transgender characters into their stories. In some cases, both DC and Marvel have retroactively categorized a longstanding character as LGBT.
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here
dc_girls_gays_theys <- clean_dc |>
  filter(!is.na(gsm))

```


```{r}
# Display results of code below this codeblock
dc_girls_gays_theys |>
  group_by(year) |>
  summarise(
    count_year=n()
  )
```
```{r}
marvel_girls_gays_they <- clean_marvel |>
  filter(!is.na(gsm))
```

```{r}
marvel_girls_gays_they |>
  group_by(year) |>
  summarise(
    count_year=n()
  )
```

### Sentence 3

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-